Evaluating computational methods for modeling off-normal operation of gas centrifuge cascades

### 2018-05-24 paper.tex
removin approx

Uranium consumption and separated fissile inventory are two important metrics
regarding to non proliferation and nuclear archaeology.  In this study, we have
been able to estimate than the cycle length uncertainty of $10\%$ implies a
variation of $3\%$ to $5\%$ on the total uranium needs uncertainty, where $\approx10\%$
on the enrichment implies a almost flat uncertainty of $2\%$.

>>>>

Uranium consumption and separated fissile inventory are two important metrics
regarding to non proliferation and nuclear archaeology.  In this study, we have
been able to estimate than the cycle length uncertainty of $10\%$ implies a
variation of $3\%$ to $5\%$ on the total uranium needs uncertainty, where about
$10\%$ on the enrichment implies a almost flat uncertainty of $2\%$.
